### 2017-06-29 README.Rmd
change p to a named vector

One categorical (2 level) variable
```
mtcars %>%
  select(am) %>%
  hypothesize(null = "point", p = .25) %>% 
  generate(reps = 100, type = "simulate") %>% 
  calculate(stat = "prop") #
```

@@

One categorical (>2 level) - GoF
```
mtcars %>%
  select(cyl) %>%
  hypothesize(null = "point", p1 = .25, p2 = .25, p3 = .50) %>% # call levels() to find order of p's
  generate(reps = 100, type = "simulate") %>%
  calculate(stat = "chisq")
```

>>>>

One categorical (2 level) variable
```
mtcars %>%
  select(am) %>%
  hypothesize(null = "point", p = c("manual" = .25)) %>% 
  generate(reps = 100, type = "simulate") %>% 
  calculate(stat = "prop") #
```

@@

One categorical (>2 level) - GoF
```
mtcars %>%
  select(cyl) %>%
  hypothesize(null = "point", p = c("4" = .5, "6" = .25, "8" = .25)) %>% # call levels() to find order of p's
  generate(reps = 100, type = "simulate") %>%
  calculate(stat = "chisq")
```
